---
title: "Mapping Water Customer Clusters"
author: "Dan Larson"
date: "4/24/2020"
output: html_document
---

### Overview

I chose to showcase this project because it had a lot of diverse elements:collaboration with multiple stakeholders, data collection, messy data,data from multiple sources,geocoding using Google API, exploratory anaylses, machine learning (segmentation),use of an additional analysis platform (ArcGIS Pro), and mapping. The final result helped inform the "Save it for the Salmon" and the ongoing "Clackamas Watershed Resiliency Project".

### Purpose

Segmentation, more specifically psychographic and behavioral segmentation, is common in the electrical utility sector but not water. I thought this would be a novel contribution. I was curious how water customer attitudes around water conservation and climate change manifested among customers with the intutition that there are different customer "archetypes". Knowing about these archetypes can help focus messaging and this project was developed as the starting point for an ongoing social marketing campaign around watershed conservation and protection.

### Research Questions

1. Do water customer attitudes show attitudinal clustering around climate change, water conservation,trust, and place attitudes.

2. Do these attitudinal clusters exhibit spatial clustering within the water service area?

## 1. Load Packages

```{r , message=FALSE, warning=FALSE}

library(tidyverse)  # Set of useful core packages
library(Hmisc)      # Misc utility package
library(mice)       # For imputation
library(cluster)    # Clustering algorithms
library(factoextra) # Extract and visualize the output of multivariate data analyses
library(psych)      # General purpose toolbox for personality, psychometric theory and experimental psychology
library(NbClust)    # Provides 30 indexes for determining the optimal number of clusters in a data set
library(clValid)    # Statistical and biological validation of clustering results
library(fpc)        # Flexible procedures for clustering - Various methods for clustering and cluster validation
library(DataExplorer) # Easy exploratory data analysis
library(corrplot)   # Makes pretty correlation plots

```

## 2. Exploratory Data Analysis (EDA)

Load Data
```{r}
load(file = "watercust_masterdata.rda")

watercust<-watercust_masterdata
```

Inspect Data
```{r}
#Initially inspect data
glimpse(watercust)


# Visualize variables in dataset
plot_str(watercust)


#Explore missing values

plot_missing(watercust)


plot_density(watercust)
```

Reduce dataset to variables of interest and convert Likert scale variables to factor
Keep attitudinal, demographic and respondent ID to join back to original dataset.

```{r}
#Change ID to key, it will make joining easier later

watercust <- watercust %>% 
  rename(key = ID) %>% 
  rename(Educ = Education1) %>% 
  rename(Politics = Political.Attitudes1) %>% 
  rename(Climate_imp = CCImpactInd_rc) %>% 
  rename(Age = Age1) 

watercust_dem<- watercust %>% 
                select(key,Age,Educ,Politics,inc_val,Climate_imp, 
                       pro_water_con,Trust_Ind,Place_Attitudes)

glimpse(watercust_dem)

```

### Visualize Correlations
```{r}
# Make a correlogram to visualize correlations among variables.

watercust_dem_cor<-watercust_dem %>% 
  select(-key)

cordta<-watercust_dem_cor
cor1 <- cor(cordta, use="pairwise.complete.obs", method="pearson")

corrplot(cor1)

# Compute the p-value of correlations
cor.mtest <- function(mat, ...) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat<- matrix(NA, n, n)
  diag(p.mat) <- 0
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j], ...)
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(watercust_dem_cor)
head(p.mat[, 1:5])

#Customize Correlogram

col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
watercust_cor<-corrplot(cor1, method="color", col=col(200),  
         type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.01, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE 
)
```

## 3. Hierarchical Cluster Analysis

We want to see what distinct clusters emerge among the attitudinal differences between water customers.
```{r}
# Subset data for clustering. Make sure 1 dataset has unique key and other does not.So it can be joined back to the spatial dataset later.

watercust_clus_wkey<- watercust_dem %>% 
  select(key,Climate_imp,pro_water_con,Trust_Ind,Place_Attitudes)

watercust_clus_nokey <- watercust_dem %>% 
  select(Climate_imp,pro_water_con,Trust_Ind,Place_Attitudes)

## Remove Missing Variables

watercust_clus_wkey <- watercust_clus_wkey[complete.cases(watercust_clus_wkey), ]
watercust_clus_nokey <- watercust_clus_nokey[complete.cases(watercust_clus_nokey), ]

## Scale prior to clustering

watercust_clus_nokey_sc <- scale(watercust_clus_nokey)

```

Determining optimal clusters using elbow method.
```{r}
library(cluster)    # clustering algorithms
library(factoextra)

fviz_nbclust(watercust_clus_nokey_sc , FUN = hcut, method = "wss")

# Method is used for determining the optimal number of clusters. "wss" is
# total within sum of squares

## Average Silhouette Method

fviz_nbclust(watercust_clus_nokey_sc, FUN = hcut, method = "silhouette")
```

Note that both the elbow method and average silhouette width show "2" as the optimal cluster solution.
Now we must test optimal number of clusters.

```{r}
library("NbClust")
set.seed(42)
res.nbclust = NbClust(watercust_clus_nokey_sc, distance = "euclidean",
                      min.nc = 2, max.nc = 10,
                      method = "ward.D", index = "all")
factoextra::fviz_nbclust(res.nbclust)+theme_minimal()

```
Note that package ```NbClust``` Uses a variety of indices (e.g. Too many to mention - See documentation here [NbClust](https://www.rdocumentation.org/packages/NbClust/versions/3.0/topics/NbClust). Optimal number of clusters is 2.

#### Hierarchical Clustering
```{r}
hc.res <- eclust(watercust_clus_nokey_sc, "hclust", k = 2, hc_metric = "euclidean", 
                 hc_method = "ward.D", graph = FALSE)


# Validating the best clustering algorithm. This is incredibly useful.

library(clValid)
watercust_clus_valid = clValid(watercust_clus_nokey_sc, nClust = 2:6,
                               clMethods = c("hierarchical","kmeans","pam"),
                               validation = "internal")
summary(watercust_clus_valid)


#Validating Clusters #
library(fpc)
dd <- dist(watercust_clus_nokey_sc, method ="euclidean")

# Statistics for hierarchical clustering
hc_stats <- cluster.stats(dd,  hc.res$cluster)
# (HCLUST) within clusters sum of squares
hc_stats$within.cluster.ss
hc_stats$clus.avg.silwidths

# Visualize Dendrogram

sp = fviz_dend(hc.res, show_labels = FALSE,
               palette = "Set1",main = "Cluster Dendrogram", theme(plot.title = element_text(hjust = 0.5)),cex = 0.75, as.ggplot = TRUE)

sp+ scale_color_manual(values=c("#FC4E07", "#2E9FDF"))

##Plot cluster solution
# Visualize HC clusters
sp2 <- fviz_cluster(hc.res, geom = "point", ellipse.type = "norm",
                    palette = c("#FC4E07", "#2E9FDF"), ggtheme = theme_minimal())
print(sp2)


# Cut tree into 2 groups and attach to original data

sub_grp <- cutree(hc.res, k = 2)
clusters <- sub_grp
clusters<-as.data.frame(clusters)

```

Join clusters back to original data. Select only relevant variables. Rename variables with unintelligible names. Then save out the data for future analyses.
```{r}
watercust_clusters<- watercust_clus_wkey %>% 
  bind_cols(clusters) %>% 
  left_join(watercust,watercust_clusters, by="key") %>% 
  select(key,Age,Educ,Politics,inc_val,Climate_imp.y,pro_water_con.y,Trust_Ind.y,Place_Attitudes.y,clusters,lon,lat) %>% 
  rename(Respondent = key)
names(watercust_clusters)<- gsub(".y", "", names(watercust_clusters))                    

# Save out the data

save(watercust_clusters, file = "watercust_clusters.RData")
```

## 4. Validate Clusters with MANOVA

We are looking to see if there is a significant difference in means between the two groups. Hence the need for MANOVA.

```{r}
library(MASS)

## Subset cluster output

man_dta<-watercust_clusters %>% 
  dplyr::select(clusters,Climate_imp,pro_water_con,Trust_Ind,Place_Attitudes)

# Perform MANOVA
set.seed(42)

man_dta$clusters = as.factor(man_dta$clusters)
Y = as.matrix(cbind(man_dta$Climate_imp, man_dta$pro_water_con, man_dta$Trust_Ind,man_dta$Place_Attitudes))
c = as.vector(man_dta$clusters)


m = manova(Y~c)
summary(m , test = "Pillai")
summary(m , test = "Wilks")
summary(m , test = "Hotelling-Lawley")
summary(m , test = "Roy")
```

We can infer from the tests that the clusters are indeed statistically different from one another.

## 5. Interpret Clusters

Now it's time to make some summary tables to interpret the clusters. To do this we will look at summary statistics, along with proportions of respondents belonging to specific segments of the repective attitudinal scales (e.g. Low Trust vs. High Trust).

```{r}
summary(watercust_clusters)

# Consider separating into two datasets then combining in the end.

watercust_clust1 <- watercust_clusters %>% 
  filter(clusters ==1)

watercust_clust2 <- watercust_clusters %>% 
  filter(clusters ==2)


```

##### Begin by looking at Cluster 1
```{r}
# Age
summary(watercust_clust1$Age)


#Income
summary(watercust_clust1$inc_val)


#Education

clust1_ed<-watercust_clust1%>% filter(!is.na(Educ))
clust1_ed <- clust1_ed%>% group_by(Educ) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total) %>% 
  filter(Educ >= 4) 

bachelor_or_higher1<-sum(clust1_ed$share)

summary(clust1_ed)
print(bachelor_or_higher1)

# Politics

watercust_clust1<-watercust_clust1 %>% filter(!is.na(Politics))

#ELSE <- TRUE
politics <- watercust_clust1%>% mutate(PoliticsSummary = 
                                         case_when( Politics >= 0 &
                                                      Politics < 2 ~ "Liberal",
                                                    Politics >= 2 & 
                                                      Politics < 3 ~ "Neutral",
                                                    Politics >= 4 ~ "Conservative")) %>% 
  dplyr::select(Politics, PoliticsSummary)
polp1 <- politics %>% group_by(PoliticsSummary) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total)
print(polp1)

# Climate Change Impact Beliefs

watercust_clust1<-watercust_clust1 %>% filter(!is.na(Climate_imp))

#ELSE <- TRUE
climate1<- watercust_clust1 %>% mutate(pnwSummary1 = 
                                         case_when( Climate_imp >= 0 &
                                                      Climate_imp < 2 ~ "Low",
                                                    Climate_imp >= 2 & 
                                                      Climate_imp< 3 ~ "Medium",
                                                    Climate_imp >= 3 ~ "High")) %>% 
  dplyr::select(Climate_imp, pnwSummary1)
pnwp1 <- climate1  %>% dplyr::group_by(pnwSummary1) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total)

print(pnwp1)

# Pro Water Conservation


watercust_clust1<-watercust_clust1 %>% filter(!is.na(pro_water_con))

clust1_prowat<- watercust_clust1 %>% mutate(pro_water_conSummary1 = 
                                              case_when( pro_water_con >= 0 &
                                                           pro_water_con < 2 ~ "Low",
                                                         pro_water_con >= 2 & 
                                                           pro_water_con < 3 ~ "Medium",
                                                         pro_water_con >= 3 ~ "High")) %>% 
  dplyr::select(pro_water_con, pro_water_conSummary1)
prowatp1 <- clust1_prowat  %>% dplyr::group_by(pro_water_conSummary1) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total)

print(prowatp1)

# Trust

watercust_clust1<-watercust_clust1 %>% filter(!is.na(Trust_Ind))

#ELSE <- TRUE
clust1_trust<- watercust_clust1 %>% mutate(Trust_IndexSummary1 = 
                                             case_when( Trust_Ind >= 0 &
                                                          Trust_Ind < 2 ~ "Low",
                                                        Trust_Ind >= 2 & 
                                                          Trust_Ind < 3 ~ "Medium",
                                                        Trust_Ind >= 3 ~ "High")) %>% 
  dplyr::select(Trust_Ind, Trust_IndexSummary1)
trustp1 <- clust1_trust  %>% dplyr::group_by(Trust_IndexSummary1) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total)

print(trustp1)

# Place Attitudes

watercust_clust1<-watercust_clust1 %>% filter(!is.na(Place_Attitudes))

#ELSE <- TRUE
pl_attitudes <- watercust_clust1 %>% mutate(AttitudeSummary1 = 
                                              case_when( Place_Attitudes >= 0 &
                                                           Place_Attitudes < 2 ~ "Low",
                                                         Place_Attitudes >= 2 & 
                                                           Place_Attitudes < 3 ~ "Medium",
                                                         Place_Attitudes >= 4 ~ "High")) %>% 
  dplyr::select(Place_Attitudes, AttitudeSummary1)
attp1 <- pl_attitudes %>% group_by(AttitudeSummary1) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total)

print(attp1)

```

##### Now move on to Cluster 2

```{r}
# Age
summary(watercust_clust2$Age)


#Income
summary(watercust_clust2$inc_val)


#Education

clust2_ed<-watercust_clust2%>% filter(!is.na(Educ))
clust2_ed <- clust2_ed%>% group_by(Educ) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total) %>% 
  filter(Educ >= 4) 

bachelor_or_higher2<-sum(clust2_ed$share)

summary(clust2_ed)
print(bachelor_or_higher2)

# Politics

watercust_clust2<-watercust_clust2 %>% filter(!is.na(Politics))

#ELSE <- TRUE
politics <- watercust_clust2%>% mutate(PoliticsSummary2 = 
                                         case_when( Politics >= 0 &
                                                      Politics < 2 ~ "Liberal",
                                                    Politics >= 2 & 
                                                      Politics < 3 ~ "Neutral",
                                                    Politics >= 4 ~ "Conservative")) %>% 
  dplyr::select(Politics, PoliticsSummary2)
polp2 <- politics %>% group_by(PoliticsSummary2) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total)
print(polp2)

# Climate Change Impact Beliefs

watercust_clust2<-watercust_clust2 %>% filter(!is.na(Climate_imp))

#ELSE <- TRUE
climate2<- watercust_clust2 %>% mutate(pnwSummary2 = 
                                         case_when( Climate_imp >= 0 &
                                                      Climate_imp < 2 ~ "Low",
                                                    Climate_imp >= 2 & 
                                                      Climate_imp< 3 ~ "Medium",
                                                    Climate_imp >= 3 ~ "High")) %>% 
  dplyr::select(Climate_imp, pnwSummary2)
pnwp2 <- climate2  %>% dplyr::group_by(pnwSummary2) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total)

print(pnwp2)

# Pro Water Conservation


watercust_clust2<-watercust_clust2 %>% filter(!is.na(pro_water_con))

clust2_prowat<- watercust_clust2 %>% mutate(pro_water_conSummary2 = 
                                              case_when( pro_water_con >= 0 &
                                                           pro_water_con < 2 ~ "Low",
                                                         pro_water_con >= 2 & 
                                                           pro_water_con < 3 ~ "Medium",
                                                         pro_water_con >= 3 ~ "High")) %>% 
  dplyr::select(pro_water_con, pro_water_conSummary2)
prowatp2 <- clust2_prowat  %>% dplyr::group_by(pro_water_conSummary2) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total)

print(prowatp2)

# Trust

watercust_clust2<-watercust_clust2 %>% filter(!is.na(Trust_Ind))

#ELSE <- TRUE
clust2_trust<- watercust_clust2 %>% mutate(Trust_IndexSummary2 = 
                                             case_when( Trust_Ind >= 0 &
                                                          Trust_Ind < 2 ~ "Low",
                                                        Trust_Ind >= 2 & 
                                                          Trust_Ind < 3 ~ "Medium",
                                                        Trust_Ind >= 3 ~ "High")) %>% 
  dplyr::select(Trust_Ind, Trust_IndexSummary2)
trustp2 <- clust2_trust  %>% dplyr::group_by(Trust_IndexSummary2) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total)

print(trustp2)

# Place Attitudes

watercust_clust2<-watercust_clust2 %>% filter(!is.na(Place_Attitudes))

#ELSE <- TRUE
pl_attitudes <- watercust_clust2 %>% mutate(AttitudeSummary2 = 
                                              case_when( Place_Attitudes >= 0 &
                                                           Place_Attitudes < 2 ~ "Low",
                                                         Place_Attitudes >= 2 & 
                                                           Place_Attitudes < 3 ~ "Medium",
                                                         Place_Attitudes >= 4 ~ "High")) %>% 
  dplyr::select(Place_Attitudes, AttitudeSummary2)
attp2 <- pl_attitudes %>% group_by(AttitudeSummary2) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(total = sum(n), share = n/total)

print(attp2)
```

Now combine results from the above calculations for Cluster 1 and Cluster 2 into table and interpret customer types.
```{r}
water_customer_types<-tribble(~Variable, ~Cluster1,~Cluster2,"MedAge",62,57,"MedIncome",87500,112500,
                              "Bachelor_or_Higher_perc",54,68,"Conservative_perc",11,3,"Liberal_perc",27,66,
                              "Neutral_perc",35,16,"Strong_Climate_Beliefs_perc",11,65,
                              "Medium_Climate_Beliefs_perc",72,34,"Weak_Climate_Beliefs_perc",17,1,
                              "Strong_Water_Conserv_perc",17,53,"Medium_Water_Conserv_perc",54,47,
                              "Weak_Water_Conserv_perc",29,0,"High_Trust_perc",2,0,"Medium_Trust_perc",26,67,
                              "Low_Trust_perc",72,31,"Medium_Place_Attachment_perc",55,42,
                              "Weak_Place_Attachment_perc",56,27)

#View results

print(water_customer_types)

```

Organize into a more stylized table
```{r}
# Print a prettier table for Markdown. Makes it more readable
library(knitr)
library(kableExtra)

water_customer_types %>%
  knitr::kable("html", align = 'clc', caption = 'Water Customer Types') %>%
  kable_styling(full_width = F, position = "center")
```

#### Interpret Tables

We can see some pretty big differences betweeen the customer types begin to emerge. Demographic differences show customer type 2 to be slightly younger, wealthier, and better educated. Customer type 2 is also more liberal with stronger beliefs about climate change and water conservation. I think a very interesting point is Trust( Trust in institutions to manager water).Cluster 1 has 72% low trust versus 31% low trust. These are very stark differences in trust between the two groups.

For segmentation to be useful it must be desciptive. Therefore "clusters" and "customer types" will now get more descriptive names. 

 **Cluster 1** ==> ***Water wasting climate skeptics***

 **Cluster 2** ==> ***Water conscious green progressives***

The names may seem silly or judgemental but they serve to make a point about the differences between the groups and paint a descriptive picture of each customer type.

## 6. Perform Hot Spot Analysis

Hot Spot Analysis is a spatial analysis technique used to identify the clustering of spatial phenomena. As previously mentioned, I was curious if "attitudinal clusters" exhibited any patterns in their spatial distriubtion that resembled clustering.

```{r}
## Pull in data and convert to Spatial Points Polygon
library(sp)
library(sf)
library(rgdal)

watercust_sp<-watercust_clusters %>% 
  dplyr::select(Respondent,clusters,lon,lat)
#Now filter out by cluster

clus1_sp<-watercust_sp %>% 
  filter(clusters==1)

clus2_sp<-watercust_sp %>% 
  filter(clusters==2)

#Convert to spatial object


coordinates(clus1_sp) <- c("lon", "lat")
coordinates(clus2_sp) <- c("lon", "lat")

# Examine the object
class(clus1_sp)
class(clus2_sp)
# Assign the projection or check if it is assigned
is.projected(clus1_sp)
is.projected(clus2_sp)

# Not projected but we knew that
proj4string(clus1_sp) <- CRS("+init=epsg:4326") # this is WGS84
proj4string(clus2_sp) <- CRS("+init=epsg:4326") # this is WGS84


# Export shapefiles for maniuplation in ArcGIS Pro

# Note: Layer already exists and I don't want to duplicate so 
# I have nullified for demonstration purposes

#writeOGR(clus1_sp, ".", "clus1", driver = "ESRI Shapefile")
#writeOGR(clus2_sp, ".", "clus2", driver = "ESRI Shapefile")

##### Perform Hot Spot Analysis in ArcGIS Pro

```

The Spatial Analysis was not performed in R, but in [ArcGIS Pro](https://www.esri.com/en-us/arcgis/products/arcgis-pro/overview). I chose to use ArcGIS Pro as I have performed this analysis previously on that platform and I was pleased with the aesthetic output of the analysis. Hot spot analysis can be performed in R using the ```hotspot``` package available in the CRAN Library. R has recently created a package [R-ArcGIS Bridge](https://r-arcgis.github.io/) to increase the spatial statistical abilities of the ArcGIS platform.

Please see the following tutorial on performing [Hot Spot Analysis using the R-ArcGIS Bridge](https://www.youtube.com/watch?v=ZGj-XX3GDP8). Note: This analysis did not employ the R-ArcGIS Bridge as it was not necessary, however new users to either platform should explore the interoperability of R and ArcGIS Pro.

## 7. Map Customer Types

```{r , warning=FALSE , message=FALSE}
library(leaflet)
library(leaflet.extras)
library(htmltools)



#Read in shapefiles generated in ArcGIS Pro

clus1htspt_poly<-readOGR(".","clus1_htspt")
clus2htspt_poly<-readOGR(".","clus2_htspt")

class(clus1htspt_poly)


# This is our base map
map<- leaflet() %>% 
  addProviderTiles("CartoDB")

# Let's save out one for base to making plotting easier later.

base_map <- map
```

Create a new variable only showing areas of 99% Confidence of a Hot Spot (High spatial clustering). Creating a factor variable will make visualization much easier.

```{r}
clus1htspt_poly$level<-clus1htspt_poly$Gi_Bin
clus2htspt_poly$level<-clus2htspt_poly$Gi_Bin

# Make a color pallette
pal1 <- colorFactor(palette = c("red"), 
                    levels = c( "3"))
pal2 <- colorFactor(palette = c("blue"), 
                    levels = c( "3"))
```

##### Water wasting climate skeptics map

```{r , warning=FALSE , message=FALSE}
c1map = addPolygons(base_map, 
                          data = clus1htspt_poly,
                          stroke = FALSE, 
                          smoothFactor = 0.2, 
                          opacity = 1,
                          color = ~pal1(clus1htspt_poly$level)) %>% 
                  addLegend("bottomright", colors= c("red"), 
                  labels=c("Water Wasting Climate Skeptics")) %>% 
  
                  addMeasure() %>% 
                  addResetMapButton()

# Print map
c1map

```

##### Water conscious green progressives map

```{r , warning=FALSE , message=FALSE}
c2map = addPolygons(base_map, 
                          data = clus2htspt_poly,
                          stroke = FALSE, 
                          smoothFactor = 0.2, 
                          opacity = 1,
                          color = ~pal2(clus2htspt_poly$level)) %>% 
                  addLegend("bottomright", colors= c("blue"), 
                  labels=c("Water conscious green progressives")) %>% 
  
                  addMeasure() %>% 
                  addResetMapButton()

#Print Map
c2map
```

